---
title: "Process Shapefiles"
author: "lkeyes"
date: "2023-04-03"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

# IMPORT FUNCTIONS
```{r}
library(rvest)
library(dplyr)

### PROJECT DIRECTORY
proj_dir <- "C:/R Working Directory/NFIB_Senate_House_Shapefiles"

### IMPORT HELPER FUNCTIONS
source(paste0(proj_dir,"/Scripts/helper_functions.R"))
```

# IMPORT FIPS DATA
```{r}
fips_data <- tidycensus::fips_codes %>%
  distinct(state, state_code, state_name) %>%
  mutate(STATE = state,
         STATECODE = state_code,
         STATENAME = state_name) %>%
  select(STATE, STATECODE, STATENAME)
```

# SENATE SHAPEFILES

## Gather the filenames from the Census <b>Upper House</b>(<i>Senate</i>) website.
```{r}
senate_url <- "https://www2.census.gov/geo/tiger/TIGER_RD18/LAYER/SLDU/"

file_names <- getFileNames(url = senate_url)
```

## Download Zip Files
```{r}
senate_dest <- paste0(proj_dir,"/Downloads/Senate/")

downloadZips(url = senate_url,
             file_destination = senate_dest,
             file_list = file_names)
```

## Extract Shapefiles from Zip
```{r}
shape_dest <- paste0(proj_dir,"/Shapefiles/Senate")

extractFiles(file_destination = senate_dest,
             extract_destination = shape_dest,
             file_list = file_names)
```

# Combine Senate Shapes and Create New Shapefile
```{r}
shp_files <- list.files(path = shape_dest,
                        pattern = "\\.shp$",
                        full.names = TRUE)


shapefile_list <- lapply(shp_files, sf::st_read)

all_shp <- do.call(sf:::rbind.sf, shapefile_list)

all_shp_mod <- all_shp %>%
  left_join(fips_data, by = c("STATEFP" = "STATECODE")) %>%
  mutate(LAT = INTPTLAT,
         LON = INTPTLON) %>%
  select(STATEFP,
         STATENAME,
         SLDUST,
         GEOID,
         NAMELSAD,
         LSAD,
         LAT,
         LON,
         geometry)

### CREATE SHP FILE
sf::st_write(all_shp_mod, paste0(proj_dir,"/Outputs/Senate_shapefile.shp"))

### CREATE GEOJSON FILE
sf::st_write(all_shp_mod, paste0(proj_dir,"/Outputs/Senate_shapefile.geojson"), driver = "GeoJSON")
```


# HOUSE SHAPEFILES

## Gather the filenames from the Census <b>Lower House</b>(<i>House</i>) website.
```{r}
house_url <- "https://www2.census.gov/geo/tiger/TIGER_RD18/LAYER/SLDL/"

file_names <- getFileNames(url = house_url)
```

## Download Zip Files
```{r}
house_dest <- paste0(proj_dir,"/Downloads/House/")

downloadZips(url = house_url,
             file_destination = house_dest,
             file_list = file_names)
```

## Extract Shapefiles from Zip
```{r}
shape_dest <- paste0(proj_dir,"/Shapefiles/House")

extractFiles(file_destination = house_dest,
             extract_destination = shape_dest,
             file_list = c(file_names, "tl_rd22_31_sldu.zip")) # THIS IS TO ADD NEBRASKA, REPLACE 22 WITH 23 NEXT YEAR
```

# Combine House Shapes and Create New Shapefile
```{r}
shp_files <- list.files(path = shape_dest,
                        pattern = "\\.shp$",
                        full.names = TRUE)


shapefile_list <- lapply(shp_files, sf::st_read)

#THIS IS TO MAKE FILENAMES FOR NEBRASKA (31) THE SAME AS ALL OTHER FILE NAMES
names(shapefile_list[[27]]) <- names(shapefile_list[[26]])

all_shp <- do.call(sf:::rbind.sf, shapefile_list)

all_shp_mod <- all_shp %>%
  left_join(fips_data, by = c("STATEFP" = "STATECODE")) %>%
  mutate(LAT = INTPTLAT,
         LON = INTPTLON) %>%
  select(STATEFP,
         STATENAME,
         SLDLST,
         GEOID,
         NAMELSAD,
         LSAD,
         LAT,
         LON,
         geometry)

### CREATE SHP FILE
sf::st_write(all_shp_mod, paste0(proj_dir,"/Outputs/House_shapefile.shp"),
             append = FALSE)

### CREATE GEOJSON FILE
sf::st_write(all_shp_mod, paste0(proj_dir,"/Outputs/House_shapefile.geojson"), driver = "GeoJSON",
             append = FALSE)
```
